### 2016-08-10 main.tex
Fix fonts on Fig. 1.  Move discussion of why we show only 1 bird to Sec. 2.3 (Quantification).  Other minor textual changes.

\begin{figure}
  \includegraphics[width=\textwidth]{Fig1}
  \caption{This image was made by superposing the spectra of our 2818
    aligned songs.  Our example detection points, $t^*_1\ldots t^*_6$,
    are shown as red lines, with the recognition regions (30 ms
    $\times$ 1--8 kHz) marked as rectangles.}
  \label{fig:song}
\end{figure}

@@

@@

The MATLAB neural network toolbox further divides our ``training'' set
into internal training, validation, and test sets.  Because we do our
own testing on a distinct and much larger data set, we instructed the
toolbox to use 80\% of its training set for training, and the
remaining 20\% for validation, with no hold-out test data.

@@

We define the accuracy of the network based on its classification
performance per frame. In order to avoid the apparent problem of every
non-detected non-syllable counting as a true negative, we also tried
defining accuracy on a per-song basis, such that a song without the
target syllable counted as a single true negative.  Computing the
optimal output thresholds on a per-frame basis resulted in higher
thresholds and thus a lower false-positive rate, with minimal
consequences to the false-negative rate, while also providing a valid
definition of false-positive rate for data streams that had not been
segmented into song-sized chunks and thus allowing easy interpretation
of false-positive rates from calls, cage noise, etc.

@@

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on a few others.  For
simplicity we present performance on 6 randomly chosen points in one
bird's song, but the results presented here are representative of
real-world performance in our lab.\marginpar{Ok?}

>>>>

\begin{figure}
  % Width: 8, Height: 3, Fonts scale: 120%
  \includegraphics[width=\textwidth]{Fig1}
  \caption{This image was made by superposing the spectra of our 2818
    aligned songs.  Our example detection points, $t^*_1\ldots t^*_6$,
    are shown as red lines, with the recognition regions (30 ms
    $\times$ 1--8 kHz) marked as rectangles.}
  \label{fig:song}
\end{figure}

@@

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on a few others.  For
simplicity, and to test robustness to imperfect choice of ``syllable'', we present performance on 6 randomly chosen points in one
bird's song.  However, the results presented here are representative of
real-world performance over many birds in our lab.

@@

The MATLAB neural network toolbox further divides our ``training'' set
into internal training, validation, and test sets.  Because we do our
own testing on a distinct data set, we instructed the
toolbox to use 80\% of its input set for training, and the
remaining 20\% for validation, with no hold-out test data.

@@

We define the accuracy of the network based on its classification
performance per frame. In order to avoid the apparent problem of every
non-detected non-syllable counting as a true negative, we also tried
defining accuracy on a per-song basis, such that a song without the
target syllable counted as a single true negave.  Computing the
optimal output thresholds on a per-frame rather than a per-song basis resulted in higher
thresholds and thus a slight reduction in both the false-positive and true-positive rates (reversible by increasing $C_n$), while also providing a valid
definition of false-positive rate for data streams that had not been
segmented into song-sized chunks and thus allowing easy interpretation
of false-positive rates from calls, cage noise, etc.

@@
